---
title: "MetaAnalysis_Plots"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

Meta-analysis was carried on three datasets Extend, EuGEI, and understanding society.METAL was used to run the meta-analysis. The script used for METAL is stored in */GWAS_bloodcelltypes/Scripts/METAL_script.txt*. The script used to clean the plink files after GWAS is stored in *GWAS_bloodcelltypes/Scripts/Adding_A2_to_plinkassoclinear_files.txt*

This report visualises the manhattan plot and qqplots of each cell type

##CD8T

```{r cd8treadin, include = FALSE, message = F, warning = F}
cd8t = read.table("/mnt/data1/GWAS_bloodcelltypes/MetaAnalysis/METAANALYSIS_CD8T_1.txt",
                  stringsAsFactors = F, header = T)

library(qqman)
library(tidyr)
cd8t_n <- cd8t
cd8t_n$ChrBp <- cd8t$MarkerName
cd8t_n <- separate(cd8t_n, ChrBp, into= c("Chr", "Bp"), sep = ":")
cd8t_n$Chr <- as.numeric(as.character(cd8t_n$Chr))
cd8t_n$Bp <- as.numeric(as.character(cd8t_n$Bp))

colnames(cd8t_n)[colnames(cd8t_n) == 'MarkerName'] <- 'SNP'
colnames(cd8t_n)[colnames(cd8t_n) == 'Chr'] <- 'CHR'
colnames(cd8t_n)[colnames(cd8t_n) == 'P.value'] <- 'P'
colnames(cd8t_n)[colnames(cd8t_n) == 'Bp'] <- 'BP'
```

```{r cd8tplot, warning = F, message = F}
bonfP<-0.05/nrow(cd8t_n)
par(mfrow = c(1,2))

manhattan(cd8t_n, genomewide = -log10(bonfP), main = "CD8T",
          suggestiveline = -log10(5e-5), logp=T, col=c("blue","yellow") )

qq(cd8t_n$P, main = "CD8T")

```

##CD4T

```{r CD4Treadin, include = FALSE, message = F, warning = F}
CD4T = read.table("/mnt/data1/GWAS_bloodcelltypes/MetaAnalysis/METAANALYSIS_CD4T_1.txt",
                  stringsAsFactors = F, header = T)

library(qqman)
library(tidyr)
CD4T_n <- CD4T
CD4T_n$ChrBp <- CD4T$MarkerName
CD4T_n <- separate(CD4T_n, ChrBp, into= c("Chr", "Bp"), sep = ":")
CD4T_n$Chr <- as.numeric(as.character(CD4T_n$Chr))
CD4T_n$Bp <- as.numeric(as.character(CD4T_n$Bp))

colnames(CD4T_n)[colnames(CD4T_n) == 'MarkerName'] <- 'SNP'
colnames(CD4T_n)[colnames(CD4T_n) == 'Chr'] <- 'CHR'
colnames(CD4T_n)[colnames(CD4T_n) == 'P.value'] <- 'P'
colnames(CD4T_n)[colnames(CD4T_n) == 'Bp'] <- 'BP'
```

```{r CD4Tplots, warning = F, message = F}
bonfP<-0.05/nrow(CD4T_n)
par(mfrow = c(1,2))

manhattan(CD4T_n, genomewide = -log10(bonfP), main = "CD4T",
          suggestiveline = -log10(5e-5), logp=T, col=c("blue","yellow") )

qq(CD4T_n$P, main = "CD4T")

```
##Bcell

```{r Bcellreadin, include = FALSE, message = F, warning = F}
Bcell = read.table("/mnt/data1/GWAS_bloodcelltypes/MetaAnalysis/METAANALYSIS_Bcell_1.txt",
                  stringsAsFactors = F, header = T)

library(qqman)
library(tidyr)
Bcell_n <- Bcell
Bcell_n$ChrBp <- Bcell$MarkerName
Bcell_n <- separate(Bcell_n, ChrBp, into= c("Chr", "Bp"), sep = ":")
Bcell_n$Chr <- as.numeric(as.character(Bcell_n$Chr))
Bcell_n$Bp <- as.numeric(as.character(Bcell_n$Bp))

colnames(Bcell_n)[colnames(Bcell_n) == 'MarkerName'] <- 'SNP'
colnames(Bcell_n)[colnames(Bcell_n) == 'Chr'] <- 'CHR'
colnames(Bcell_n)[colnames(Bcell_n) == 'P.value'] <- 'P'
colnames(Bcell_n)[colnames(Bcell_n) == 'Bp'] <- 'BP'
```

```{r Bcellplot, warning = F, message = F}
bonfP<-0.05/nrow(Bcell_n)
par(mfrow = c(1,2))

manhattan(Bcell_n, genomewide = -log10(bonfP), main = "Bcell",
          suggestiveline = -log10(5e-5), logp=T, col=c("blue","yellow") )

qq(Bcell_n$P, main = "Bcell")

```
##NK

```{r NKreadin, include = FALSE, message = F, warning = F}
NK = read.table("/mnt/data1/GWAS_bloodcelltypes/MetaAnalysis/METAANALYSIS_NK_1.txt",
                  stringsAsFactors = F, header = T)

library(qqman)
library(tidyr)
NK_n <- NK
NK_n$ChrBp <- NK$MarkerName
NK_n <- separate(NK_n, ChrBp, into= c("Chr", "Bp"), sep = ":")
NK_n$Chr <- as.numeric(as.character(NK_n$Chr))
NK_n$Bp <- as.numeric(as.character(NK_n$Bp))

colnames(NK_n)[colnames(NK_n) == 'MarkerName'] <- 'SNP'
colnames(NK_n)[colnames(NK_n) == 'Chr'] <- 'CHR'
colnames(NK_n)[colnames(NK_n) == 'P.value'] <- 'P'
colnames(NK_n)[colnames(NK_n) == 'Bp'] <- 'BP'
```

```{r NKplot, warning = F, message = F}
bonfP<-0.05/nrow(NK_n)
par(mfrow = c(1,2))

manhattan(NK_n, genomewide = -log10(bonfP), main = "NK",
          suggestiveline = -log10(5e-5), logp=T, col=c("blue","yellow") )

qq(NK_n$P, main = "NK")

```
##Neu

```{r Neureadin, include = FALSE, message = F, warning = F}

Neu <- read.table("/mnt/data1/GWAS_bloodcelltypes/MetaAnalysis/METAANALYSIS_Neu_1.txt",
                  stringsAsFactors = F, header = T)

library(qqman)
library(tidyr)
Neu_n <- Neu
Neu_n$ChrBp <- Neu$MarkerName
Neu_n <- separate(Neu_n, ChrBp, into= c("Chr", "Bp"), sep = ":")
Neu_n$Chr <- as.numeric(as.character(Neu_n$Chr))
Neu_n$Bp <- as.numeric(as.character(Neu_n$Bp))

colnames(Neu_n)[colnames(Neu_n) == 'MarkerName'] <- 'SNP'
colnames(Neu_n)[colnames(Neu_n) == 'Chr'] <- 'CHR'
colnames(Neu_n)[colnames(Neu_n) == 'P.value'] <- 'P'
colnames(Neu_n)[colnames(Neu_n) == 'Bp'] <- 'BP'
```

```{r Neuplot, warning = F, message = F}
bonfP<-0.05/nrow(Neu_n)
par(mfrow = c(1,2))

manhattan(Neu_n, genomewide = -log10(bonfP), main = "Neu",
          suggestiveline = -log10(5e-5), logp=T, col=c("blue","yellow") )

qq(Neu_n$P, main = "Neu")

```


##Gran

```{r Granreadin, include = FALSE, message = F, warning = F}
Gran = read.table("/mnt/data1/GWAS_bloodcelltypes/MetaAnalysis/METAANALYSIS_Gran_1.txt",
                  stringsAsFactors = F, header = T)

library(qqman)
library(tidyr)
Gran_n <- Gran
Gran_n$ChrBp <- Gran$MarkerName
Gran_n <- separate(Gran_n, ChrBp, into= c("Chr", "Bp"), sep = ":")
Gran_n$Chr <- as.numeric(as.character(Gran_n$Chr))
Gran_n$Bp <- as.numeric(as.character(Gran_n$Bp))

colnames(Gran_n)[colnames(Gran_n) == 'MarkerName'] <- 'SNP'
colnames(Gran_n)[colnames(Gran_n) == 'Chr'] <- 'CHR'
colnames(Gran_n)[colnames(Gran_n) == 'P.value'] <- 'P'
colnames(Gran_n)[colnames(Gran_n) == 'Bp'] <- 'BP'
```

```{r Granplot, warning = F, message = F}
bonfP<-0.05/nrow(Gran_n)
par(mfrow = c(1,2))

manhattan(Gran_n, genomewide = -log10(bonfP), main = "Gran",
          suggestiveline = -log10(5e-5), logp=T, col=c("blue","yellow") )

qq(Gran_n$P, main = "Gran")

```


##Eos

```{r Eosreadin, include = FALSE, message = F, warning = F}
Eos = read.table("/mnt/data1/GWAS_bloodcelltypes/MetaAnalysis/METAANALYSIS_Eos_1.txt",
                  stringsAsFactors = F, header = T)

library(qqman)
library(tidyr)
Eos_n <- Eos
Eos_n$ChrBp <- Eos$MarkerName
Eos_n <- separate(Eos_n, ChrBp, into= c("Chr", "Bp"), sep = ":")
Eos_n$Chr <- as.numeric(as.character(Eos_n$Chr))
Eos_n$Bp <- as.numeric(as.character(Eos_n$Bp))

colnames(Eos_n)[colnames(Eos_n) == 'MarkerName'] <- 'SNP'
colnames(Eos_n)[colnames(Eos_n) == 'Chr'] <- 'CHR'
colnames(Eos_n)[colnames(Eos_n) == 'P.value'] <- 'P'
colnames(Eos_n)[colnames(Eos_n) == 'Bp'] <- 'BP'
```

```{r Eosplot, warning = F, message = F}
bonfP<-0.05/nrow(Eos_n)
par(mfrow = c(1,2))

manhattan(Eos_n, genomewide = -log10(bonfP), main = "Eos",
          suggestiveline = -log10(5e-5), logp=T, col=c("blue","yellow") )

qq(Eos_n$P, main = "Eos")

```


##Mono

```{r Monoreadin, include = FALSE, message = F, warning = F}
Mono = read.table("/mnt/data1/GWAS_bloodcelltypes/MetaAnalysis/METAANALYSIS_Mono_1.txt",
                  stringsAsFactors = F, header = T)

library(qqman)
library(tidyr)
Mono_n <- Mono
Mono_n$ChrBp <- Mono$MarkerName
Mono_n <- separate(Mono_n, ChrBp, into= c("Chr", "Bp"), sep = ":")
Mono_n$Chr <- as.numeric(as.character(Mono_n$Chr))
Mono_n$Bp <- as.numeric(as.character(Mono_n$Bp))

colnames(Mono_n)[colnames(Mono_n) == 'MarkerName'] <- 'SNP'
colnames(Mono_n)[colnames(Mono_n) == 'Chr'] <- 'CHR'
colnames(Mono_n)[colnames(Mono_n) == 'P.value'] <- 'P'
colnames(Mono_n)[colnames(Mono_n) == 'Bp'] <- 'BP'
```

```{r Monoplot, warning = F, message = F}
bonfP<-0.05/nrow(Mono_n)

par(mfrow = c(1,2))
manhattan(Mono_n, genomewide = -log10(bonfP), main = "Mono",
          suggestiveline = -log10(5e-5), logp=T, col=c("blue","yellow"))

qq(Mono_n$P, main = "Mono")

```
